# R Methods and how "to\`s":   

## How to add Lorem ipsum paragraphs in r markdow.   

**lorem::ipsum()** link [here](https://github.com/gadenbuie/lorem) to see all examples.\
\* Quickly generate lorem ipsum placeholder text with **lorem::ipsum()**.\
\* Easy to integrate in RMarkdown documents.\
\* Includes an RStudio addin to insert lorem ipsum into the current document.

First install

```{r eval=FALSE}
install.package("devtools")
devtools::install_github("gadenbuie/lorem")

# If devtools can not be installed. 
# Install in terminal: 
# brew install libgit2

#Then in R
# install.packages("devtools")
# install.packages("usethis")

```

If error: 
` Error: Failed to install 'lorem' from GitHub:
  ERROR: failed to lock directory ‘/Library/Frameworks/R.framework/Versions/4.1/Resources/library’ for modifying
**Try removing ‘/Library/Frameworks/R.framework/Versions/4.1/Resources/library/00LOCK’** `

**Usage**: The addin allows you to specify the number of desired paragraphs and sentences.

R Markdown\
**Call lorem::ipsum() in an inline R chunk in R Markdown.**

```{r eval=FALSE}
`r lorem::ipsum(paragraphs = 2)`  
```

**Place the scrip with "\`\`" (inline code) to call the function. ex.**

```{r eval=FALSE}
`r lorem::ipsum(paragraphs = 1)`  
```

**You can control the number of paragraphs and sentences per paragraph.**

```{r eval=FALSE}
`r lorem::ipsum(paragraphs = 3, sentences = c(1, 2, 3))`  
```

You can also adjust the avg_words_per_sentence to create long or short paragraphs.

```{r eval=FALSE}
`r lorem::ipsum(2, avg_words_per_sentence = 3)`  
`r lorem::ipsum(1, avg_words_per_sentence = 20)`  
```

**Everywhere Else**\
Generate lorem ipsum anywhere else using lorem::ipsum() or lorem::ipsum_words().

```{r eval=FALSE}
ipsum_items <- replicate(5, lorem::ipsum_words(5))
cat(paste("-", ipsum_items), sep = "\n")
```

------------------------------------------------------------------------

## How to insert colummns in r markdown.

Description of the methods in this [Link](https://stackoverflow.com/questions/31753897/2-column-section-in-r-markdown).

Put the following in the **css file or directly in rmarkdown.**

> **It is better to add directly to the style.css file for it to work properly.**

```{css }
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>
```

### 3 Columns + loremipsum example

Code:

```{ruby, eval=FALSE }
<div class="col3">
**1. paragraphs = 1**   
`r lorem::ipsum()`  
**2. paragraphs = 3, sentences = c(1, 2, 3)**    
`r lorem::ipsum(paragraphs = 3, sentences = c(1, 2, 3))`  
**3. paragraphs = 2, avg_words_per_sentence = 3**     
`r lorem::ipsum(2, avg_words_per_sentence = 3)`  
**4.** four.    
**5.** five.      
**6.** six.      
**7.** seven.     
**8.** eight.    
**9.** nine.     
</div>
```

Result

::: {.col3}
**1. paragraphs = 1**\
`r lorem::ipsum()`\
**2. paragraphs = 3, sentences = c(1, 2, 3)**\
`r lorem::ipsum(paragraphs = 3, sentences = c(1, 2, 3))`\
**3. paragraphs = 2, avg_words_per_sentence = 3**\
`r lorem::ipsum(2, avg_words_per_sentence = 3)`\
**4.** four.\
**5.** five.\
**6.** six.\
**7.** seven.\
**8.** eight.\
**9.** nine.
:::

### 2 Columns examples.

Code: (Erase the "()" in the {} section, it should be **{r}** only)

```{ruby, eval=FALSE}
<div class="col2">  
head(mtcars)
tail(mtcars)```  
</div>
```

Result:

::: {.col2}
```{r}
head(mtcars)
tail(mtcars)
```
:::

From here the columns are released.

------------------------------------------------------------------------

## How to Find the indices of lines in Markdown that are prose (not balanced).

[Link1](https://cran.r-project.org/web/packages/xfun/xfun.pdf), [Link2](https://rdrr.io/cran/xfun/man/prose_index.html)

**Prose_index** Find the indices of lines in Markdown that are prose (not code blocks).

**Description**\
Filters out the indices of lines between code block fences such as \`\`\` (could be three or four or more backticks).

**Usage**

```{r eval=FALSE}
library(xfun)
## ??xfun
prose_index("```", warn = TRUE)
prose_index(c("a", "```", "b", "```", "c"))
prose_index(c("a", "````", "```r", "1+1", "```", "````", "c"))

```

**Value:** An integer vector of indices of lines that are prose in Markdown. **Note:** If the code fences are not balanced (e.g., a starting fence without an ending fence), this function will treat all lines as prose.

Still DO NOT UNDERSTAND HOW IT WORKS AND WHAT THE OUTCOME MEANS.

------------------------------------------------------------------------

## How to DISCHARGE git commits to avoid conflicts (Special circumstances).

Apparently it is not possible to discard changes made in \>environment \>Git tab. (At least I did not found a way yet).

The only way Discard is by:

1.  going to the **GitHub desktop app**,\
2.  Select the correct repository from where to remove the changes.\
3.  Select all the changed files (command + A)\
4.  Right click over the selected changes.\
5.  Select **discard selected changes** and click on OK.


## How to create an r bookdown and link with github paages.   

1. Create a bookdown project in R.    
// Session > New session >    
// File > New project > ..[].. > New Directory > Book Project using bookdown >   
// Tools > Project options (Or: // [Git] > Project Setup ) > Git/SVN > Version control System: Git >   
1. Open GitHub > Add > Select Project forlder in ~Documents/GitHub  > Publish branch >   
1. Open Github in brawser > Settings > Pages > Git Pages > Source > » Master > »/docs > Saves.   

In the Projects files.    

README.md   
R Markdown and **bookdown** (https://github.com/rstudio/bookdown). Bioinformatics RNA-seq project.     

_bookdown.yml:   
**Important**:   
> Here is very important to **add the "output_dir: "docs".**

```{r, eval=FALSE}
book_filename: "Bioinformatics_RNA-seq"
delete_merged_file: true
output_dir: "docs"
language:
  ui:
    chapter_name: "Chapter 01"


```

_output.yml.   
```{r eval=FALSE}
bookdown::gitbook:
  css: style.css
  config:
    toc:
      before: |
        <li><a href="./">Bio-Informatics</a></li>
      after: |
        <li><a href="https://github.com/rstudio/bookdown" target="blank">Published with bookdown</a></li>
    download: ["pdf", "epub"]

```

Index.Rmd:   
```{r eval=FALSE}
--- 
title: "Bioinformatics_RNA-seq"
author: "J. Marcelo Rosales R."
date: '**Created:** 2021-08-10;  **Update:** 2021-08-20; **Date:** `r Sys.Date()`' 
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "RNA-seq notes and trials"
---
```


Also in Index.Rmd. 
**Important**: To avoid the  **File packages.bib not found in resource path** error.  
Paste the following code after the md heading.  knitr expects all paths to be either absolute or relative to your current R working directory.    


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```  



## How to change the created date or modify the date on MAC.  

Resume
```{bash, eval=FALSE}
# To see the manual of the touch command:
man touch

# To see the metadata of the file use:
mdls Path/file # for path darg and drop file from finder to terminal

# modify creation date with touch -flag YYYYMMDDhhmm
# t for creation date, but it changes modified date
touch -t 201911252028 GH010193.MP4 
touch -m 201911252028 GH010193.MP4 # Changes modified date to current date not input
touch -mt 201911252028 GH010193.MP4 # Changes modified date only, not created date

# Entire Folder
touch -t 201911252028 /*

# Only the folder (not file in folder)
touch -t 201908131200  /Volumes/homes/RosalesJM/SynDS220/Media\ Libraries/Video/GoProH7/untitled\ folder 
# If folder is created for the first time, then -t flag will change both, created and modified dates

# To change created date using SetFile 
man SetFile
# Changind created date of one file. 
SetFile -d "11/10/2019 18:22"  GH010185.MP4 # if pwd is same as files
SetFile -d "11/10/2019 18:22" /Volumes/homes/RosalesJM/SynDS220/Media\ Libraries/Video/GoProH7/GH010185.MP4  # pwd does not matter.

# Changing created date of several  files at the same time. 
SetFile -d "11/10/2019 18:22"  GH010185.MP4 GH010186.MP4 GH010187.MP4 # etc..

SetFile -d "11/10/2019 18:44" /Volumes/HD-PCFSU3-A/Movies/VideosU/gopro\ H7/20191110-Leica\ Microscope/GH010191.MP4 /Volumes/HD-PCFSU3-A/Movies/VideosU/gopro\ H7/20191110-Leica\ Microscope/GH010192.MP4 /Volumes/homes/RosalesJM/SynDS220/Media\ Libraries/Video/GoProH7/GH010191.MP4 # etc..


# If gray-out and been used by OS
SetFile -c "" -t "" path/to/file.mov * # *: all files in the pwd
```

Videos:
https://www.youtube.com/watch?v=b33ir6FZMlY


Creation Date / Modified Date
If you are changing the creation date attribute will also change the modified date attribute.

1.  to open Terminal application (/Applications/Utilities/Terminal.app)
      ( cmd + space ) to open “Spotlight Search”
      Type in “Terminal” press enter

2. Explain what is for creation date and modified date
       -t = for created date 
       -mt = for modified date

Replace YYYYMMDDhhmm with the desired date information:

“touch -t YYYYMMDDhhmm “
“touch -mt YYYYMMDDhhmm ”
( copy without the question marks!! )


3. Type the following in the command line “Do not press enter/return” !

Example:  22nd May 1986 2:24 pm ( 14:24 ) or 22.05.1986 2:24 pm

-“touch -t 198605221424 “

-“touch -mt 198605221424 “

To see the manual of the touch command:
`man touch`

To see the metadata of the file use:
`mdls Path/file`


touch -t is used to change the modification date now onwards

Do not forget the space otherwise you get a message 
( touch: out of range or illegal time specification: [[CC]YY]MMDDhhmm[.SS] )


4. Open Finder locate the file you wish to modify. 
    Drag and drop the file into the Terminal window, the file, and path will be added to the end of the line.

Here is an example of what the line should look like: 

Option 1: Single file
touch -t 198605221424 /Users/maikkleinert/Desktop/How\ to\ modify\ date\ or\ time/all\ in\ one\ pdf_by_MaikKleinert.com.pdf


Option 2: Multiple file
touch -t 198605221424 /Users/maikkleinert/Desktop/How\ to\ modify\ date\ or\ time/Concert-Online-Course_by_MaikKleinert.com.jpg /Users/maikkleinert/Desktop/How\ to\ modify\ date\ or\ time/Film\ Photo\ Collective_by_MaikKleinert.com.png /Users/maikkleinert/Desktop/How\ to\ modify\ date\ or\ time/Instagram\ @MaikKleinert.png

Option 3: Folder ( Do not forget  the /*)
touch -t 198605221424 /Users/maikkleinert/Desktop/How\ to\ modify\ date\ or\ time\ FOLDER /*

Then press enter!
Done 

To check the date ( right click on file and “Get Info” ) or press ( cmd+I )

Also you can Add /* to the end of the command. If you’re only targeting a specific file type include its extension (e.g. /*.jpg).
Example:
touch -t 198605221424 /Users/maikkleinert/Desktop/How\ to\ modify\ date\ or\ time\ FOLDER/*.jpgor 
touch -t 198605221424 /Users/maikkleinert/Desktop/How\ to\ modify\ date\ or\ time\ FOLDER/*.pdf

### *Update* 
If It's not working then try this out
creation date:   (angle Bracket right)  Setfile -d '08/31/2019 11:00:00' (angle bracket left)file.txt(angle Bracket right)

SetFile -d 'MM/DD/YYYY' drag and drop file here (changing Creation date of file)

EXAMPLES
This command line sets the creation date of all .MP4 files in the "present" folder" (first go to the folder were the files are located with `cd path/to/folder`then type:
`SetFile -d "05/25/2021 10:00" *.MP4`

This command line sets the modification date of "myFile":
`SetFile -m "8/4/2001 16:13" myFile`

**If file in external HD, greyed out and won't open: "this item is used by Mac OS X"**
The file won't open, with QuickTime, with the following error message:

Item "file.mov" is used by Mac OS X and cannot be opened.
This is a common issue which happens when the file's type and creator attributes are modified by Finder when its writing files, if these attributes aren't restored back to the original values by Finder at the end of its write action, those files won't be accessible to the user.

Running this command will remove the creator and type attributes set by Finder,

SetFile -c "" -t "" path/to/file.mov
Note: If the above command is not found, try installing Xcode command line tool and try the above command again,

## How to copy all files with a certain extension from all subdirectories  

```{bash, eval=FALSE}
# Go to the folder containing the subfolders and files.
cd /Volumes/1TBRedBuffal/new\ vids/DVF/HDVF

# Copy all the files with extension M2T
cp **/*.M2T /Volumes/homes/RosalesJM/SynDS220/Media\ Libraries/Video/20211014-ProArch_IG/Raw-M2T

```


Option 1:  

`find . -name \*.xls -exec cp {} newDir \;`  

in which cp is executed for each filename that find finds, and passed the filename correctly. Here's more info on this technique.  

Option 2:  
Instead of all the above, you could use zsh and simply type  

`cp **/*.xls target_directory`  
zsh can expand wildcards to include subdirectories and makes this sort of thing very easy.  



