# R Methods and how to`s:  

## How to add Lorem ipsum paragraphs in r markdow.  

**lorem::ipsum()**  link [here](https://github.com/gadenbuie/lorem) to see all examples.  
* Quickly generate lorem ipsum placeholder text with **lorem::ipsum()**.  
* Easy to integrate in RMarkdown documents.  
* Includes an RStudio addin to insert lorem ipsum into the current document.  

First install  
```{r eval=FALSE}
# install.package("devtools")
devtools::install_github("gadenbuie/lorem")

# If devtools can not be installed. 
# Install in terminal: 
# brew install libgit2

#Then in R
# install.packages("devtools")
# install.packages("usethis")

```
**Usage**: The addin allows you to specify the number of desired paragraphs and sentences.  

R Markdown  
**Call lorem::ipsum() in an inline R chunk in R Markdown.**
```{r eval=FALSE}
`r lorem::ipsum(paragraphs = 2)`  
```
**Place the scrip with "``" (inline code) to call the function. ex.**
```{r eval=FALSE}
`r lorem::ipsum(paragraphs = 1)`  
```


**You can control the number of paragraphs and sentences per paragraph.**  
```{r eval=FALSE}
`r lorem::ipsum(paragraphs = 3, sentences = c(1, 2, 3))`  
```


You can also adjust the avg_words_per_sentence to create long or short paragraphs.  
```{r eval=FALSE}
`r lorem::ipsum(2, avg_words_per_sentence = 3)`  
`r lorem::ipsum(1, avg_words_per_sentence = 20)`  
```


**Everywhere Else**    
Generate lorem ipsum anywhere else using lorem::ipsum() or lorem::ipsum_words().  
```{r eval=FALSE}
ipsum_items <- replicate(5, lorem::ipsum_words(5))
cat(paste("-", ipsum_items), sep = "\n")
```  

****************************************************************************  

## How to insert colummns in r markdown.  

Description of the  methods in this [Link](https://stackoverflow.com/questions/31753897/2-column-section-in-r-markdown).  

Put the following in the **css file or directly in rmarkdown.**  

> **It is better to add directly to the style.css file for it to work properly.**  

```{css }
<style>
  .col2 {
    columns: 2 200px;         /* number of columns and width in pixels*/
    -webkit-columns: 2 200px; /* chrome, safari */
    -moz-columns: 2 200px;    /* firefox */
  }
  .col3 {
    columns: 3 100px;
    -webkit-columns: 3 100px;
    -moz-columns: 3 100px;
  }
</style>
```  

### Columns + loremipsum example
Code:
```{ruby, eval=FALSE }
<div class="col3">
**1. paragraphs = 1**   
`r lorem::ipsum()`  
**2. paragraphs = 3, sentences = c(1, 2, 3)**    
`r lorem::ipsum(paragraphs = 3, sentences = c(1, 2, 3))`  
**3. paragraphs = 2, avg_words_per_sentence = 3**     
`r lorem::ipsum(2, avg_words_per_sentence = 3)`  
**4.** four.    
**5.** five.      
**6.** six.      
**7.** seven.     
**8.** eight.    
**9.** nine.     
</div>
```

Result

<div class="col3">
**1. paragraphs = 1**   
`r lorem::ipsum()`  
**2. paragraphs = 3, sentences = c(1, 2, 3)**    
`r lorem::ipsum(paragraphs = 3, sentences = c(1, 2, 3))`  
**3. paragraphs = 2, avg_words_per_sentence = 3**     
`r lorem::ipsum(2, avg_words_per_sentence = 3)`  
**4.** four.    
**5.** five.      
**6.** six.      
**7.** seven.     
**8.** eight.    
**9.** nine.     
</div>

### This section will have two columns
Code:  (Erase the "()" in the {} section, it should be **{r}** only)
```{ruby, eval=FALSE}
<div class="col2">  
```{(r)}
head(mtcars)
tail(mtcars)```  
</div>
```

Result:

<div class="col2">  
```{r}
head(mtcars)
tail(mtcars)
```  
</div>

From here the columns are released. 

****************************************************************************  

## How to Find the indices of lines in Markdown that are prose (not balanced).  
[Link1](https://cran.r-project.org/web/packages/xfun/xfun.pdf), [Link2](https://rdrr.io/cran/xfun/man/prose_index.html)  

**Prose_index** Find the indices of lines in Markdown that are prose (not code blocks).  

**Description**  
Filters out the indices of lines between code block fences such as ``` (could be three or four or more backticks).  

**Usage**  
```{r eval=FALSE}
library(xfun)
## ??xfun
prose_index("```", warn = TRUE)
prose_index(c("a", "```", "b", "```", "c"))
prose_index(c("a", "````", "```r", "1+1", "```", "````", "c"))

```  

**Value:** An integer vector of indices of lines that are prose in Markdown.
**Note:**  If the code fences are not balanced (e.g., a starting fence without an ending fence), this function will treat all lines as prose.  

Still DO NOT UNDERSTAND HOW IT WORKS AND WHAT THE OUTCOME MEANS.  

****************************************************************************  

##  How to DISCHARGE git commits to avoid conflicts (Special circumstances).  

Apparently it is not possible to discard changes made in >environment >Git tab. (At least I did not found a way yet).  

The only way Discard is by:  

1. going to the **GitHub desktop app**,  
1. Select the correct repository from where to remove the changes.   
1. Select all the changed files (command + A)  
1. Right click over the selected changes.  
1. Select **discard selected changes** and click on OK.   

